---
title: "Day 4 Interactive"
format: html
editor: visual
---

<<<<<<< HEAD
## Functions
=======
## Functions 
>>>>>>> 2b0277bb38618df17f7d9f1da362535011274733

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
}
```

```{r}
double_value(13.4)

monthly_income <- c(42.5, 61.75, 89.5)

double_value(monthly_income)
```

**Example 1**

Create a function that returns an awesome restaurant name given a cool animal and your favorite food.

```{r}

restaurant_name <- function(animal, food) {
  print(paste0(animal, food))
}

restaurant_name("tiger", "Apples")
```

**Example 2**

Given temp in degrees F, write a function that converts it to Celsius.

```{r}
f_to_c <- function(f_temp) {
  print((f_temp - 39) * (5/9))
}

f_to_c(50)
```

**Example 3**

Create a function that given inputs of age and hometowns, return "I am \_\_ years old, and I'm from \_\_\_"

```{r}

home_town <- function(age, town) {
  print(paste("I am", age, "years old, and I'm from", town))
}

home_town(13, "NYC")
```

## Function with conditionals

**Example 1**

```{r}
calculate_animal_age <- function(species, age_human_yrs) {
  if (species == "dog") {
    age_human_yrs * 7
  } else if (species == "goat") {
    age_human_yrs * 4.7
  }
}

# to break it
calculate_animal_age("whale", 7)

# solution - add another else condition 
calculate_animal_age <- function(species, age_human_yrs) {
  if (species == "dog") {
    age_human_yrs * 7
  } else if (species == "goat") {
    age_human_yrs * 4.7
  } else print("Please enter goat or dog!")
}

calculate_animal_age("whale", 7)
```

**Example 2**

Write a function that will return, given temp in Kelvin, if a user selects "metric" to the scale then return degrees C, or if they select "english" then return degrees in F.

```{r}

convert_kelvin_to_f_c <- function(temp_kelvin, scale) {
  if (scale == "metric") {
    print(temp_kelvin - 273.15)
} else if (scale == "english") {
    print((temp_kelvin - 273.15) * 9/5 + 32)
  }
}

convert_kelvin_to_f_c(50, "metric")
```
